---
title: "Transect Report"
author: ''
date: ''
output:
  word_document: default
  pdf_document: default
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, messages= FALSE, warning= FALSE, comment = NA, fig.width = 7, fig.height=7)
#knitr::opts_knit$set(root.dir=normalizePath('../'),fig.align="center")
#devtools::install_github("haozhu233/kableExtra")

options(scipen=999, digits=2)

library("lubridate")
library("ggplot2")
library("dplyr")
library("viridis")
library("tidyverse")
library("scales")
library("waterData")
library("gridExtra")
library("cowplot")
library('ggpubr')
library("reshape2")

#sourcing the function
source("script/oyster_functions.R")
```

```{r organize, include= FALSE}
data <- read.csv("data/oys_transect/transect_data.csv", header= TRUE)
org_data <- organizeData(data)
cal_den<- calculateCountsDensity(data,org_data)

### days sampled for all time
total_days <- length(unique(org_data$date))

total_days_22 <- length(unique(org_data$date[org_data$date > "2020-08-01"]))
```

# Overview
This report provides summary statistics and figures for ongoing transect sampling. The first section of the report focuses on the current sampling (Winter 2020-2021) and how the collected data compare to last year's sampling (Winter 2019-2020). So far `r total_days_22` days have been sampled this season. The second half of the report gives summaries of all of the data that have been collected since the beginning of the project (`r head(org_data$date, 1)`). In total, `r total_days` days have been sampled over this entire project. 

## Definition of Localities
\begingroup\Large
| LOCALITY | LOCATION        |  
|:---------|----------------:|
| BT       | Big Trout       |   
| CK       | Cedar Key       |  
| CR       | Corrigan's Reef | 
| HB       | Horseshoe Beach | 
| LC       | Lone Cabbage    | 
| LT       | Little Trout    |  
| NN       | No Name         | 
\endgroup


## Definition of Strata
\begingroup\Large
| STRATA  | DEFINITION              |  
|:--------|------------------------:|
| Y_N    | Yes Harvest, No Rock     |   
| Y_Y    | Yes Harvest, Yes Rock    |  
| N_N    | No Harvest, No Rock      | 
| N_Y    | No Harvest, Yes Rock     | 
| N_PILOT| No Harvest, Pilot Rocks  |  
\endgroup



# Current Sampling
Here, we provide a progress bar showing how much of the sampling has been completed for this season, plus summary tables and plots comparing live counts and density of oysters between this current season and last year. **The current sampling period is period 22, and last year's sampling period is period 20.** 

```{r progress_bar, echo=FALSE,comment=NA, fig.width = 7, fig.height = 6}
progress(org_data)
```

```{r, include= FALSE}
s <- subset(org_data, org_data$period == 22)

  s2 <- aggregate(tran_length ~ station + strata + transect, data = s, FUN = max)
  s3 <- aggregate(tran_length ~ strata, data = s2, FUN = 'sum')
  
  Y_NA <- 424
  N_NA <- 543
  N_YA <- 1183
  Y_YA <- 1149
  
  Total<- 3299

  Y_N_sub_total<- min(Y_NA, s3$tran_length[s3$strata == "Y_N"])
  N_N_sub_total<- min(N_NA, s3$tran_length[s3$strata == "N_N"])
  Y_Y_sub_total<- min(Y_YA, s3$tran_length[s3$strata == "Y_Y"])
  N_Y_sub_total<- min(N_YA, s3$tran_length[s3$strata == "N_Y"])
  
  
```


| STRATA  | Meters Completed        |  
|:--------|------------------------:|
| Y_N    | `r Y_N_sub_total`        |   
| Y_Y    | `r Y_Y_sub_total`        |  
| N_N    | `r N_N_sub_total`        | 
| N_Y    |`r N_Y_sub_total`         | 
  
Table - Displaying the total meters surveyed during period 22 per strata.


## Summary Plots for Periods 18, 20 and 22
  
```{r 2022_local, echo=FALSE,comment=NA}

# Colors for periods
#18- CC79A7 (pink)
#20-E69F00 (orange)
#22-56B4E9 (blue)


current_plot<- cal_den

current_plot$period <- factor(current_plot$period, levels = c("18", "20", "22"))
current_plot %>% 
  filter(period== 18 | period== 20 | period==22) %>% 
  ggplot( aes(y= density, fill=as.factor(period))) +
  geom_boxplot()+
  ylab("Oyster density per m^2")+
  labs(title= "Live Oyster Density by Locality for Periods 18, 20, and 22", fill= "Period") +
  scale_fill_manual(values=c("#CC79A7", "#E69F00", "#56B4E9"))+
  theme(legend.position="right",panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"))+
  facet_wrap(~locality)

```
Figure- Calculated live oyster density by locality for periods 18 (Winter 2018-2019), 20 (Winter 2019-2020) and 22 (Winter 2020-2021) with the last sample date of period 22 as `r tail(org_data$date, 1)`.
\newpage

```{r,echo=FALSE,comment=NA}

current_plot<- cal_den

current_plot$period <- factor(current_plot$period, levels = c("18", "20", "22"))

current_plot %>% 
  filter(period== 18 | period== 20 | period==22) %>% 
  ggplot( aes( y= density_dead, fill=as.factor(period))) +
  geom_boxplot() +
  ylab("Oyster density per m^2")+
  labs(title= "Dead Oyster Density by Locality for Periods 18, 20, and 22", fill= "Period") +
  scale_fill_manual(values=c("#CC79A7", "#E69F00", "#56B4E9"))+
  theme(legend.position="right",panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid")) +
  facet_wrap(~locality)
```
Figure- Calculated dead oyster density by locality for periods 18 (Winter 2018-2019), 20 (Winter 2019-2020) and 22 (Winter 2020-2021) with the last sample date of period 22 as `r tail(org_data$date, 1)`.
\newpage

```{r 2022_strata,echo=FALSE,comment=NA }

current_plot<- cal_den

current_plot$period <- factor(current_plot$period, levels = c("18", "20", "22"))
current_plot$strata <- factor(current_plot$strata, levels = c("Y_Y", "Y_N", "N_Y", "N_N", "N_PILOT"))

current_plot %>% 
  filter(period== 18 | period== 20 | period==22) %>% 
  ggplot( aes(y= density, fill=as.factor(period))) +
  geom_boxplot() +
  ylab("Oyster density per m^2")+
  labs(title= "Live Oyster Density by Strata for Periods 18, 20 and 22", fill= "Period") +
  scale_fill_manual(values=c("#CC79A7", "#E69F00", "#56B4E9"))+
  theme(legend.position="right",panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid")) +
    facet_wrap(~strata, ncol= 2)

```
Figure- Calculated live oyster density by strata for  periods 18 (Winter 2018-2019), 20 (Winter 2019-2020) and 22 (Winter 2020-2021) with the last sample date of period 22 as `r tail(org_data$date, 1)`.
\newpage


```{r,echo=FALSE,comment=NA}
current_plot<- cal_den

current_plot$period <- factor(current_plot$period, levels = c("18", "20", "22"))
current_plot$strata <- factor(current_plot$strata, levels = c("Y_Y", "Y_N", "N_Y", "N_N", "N_PILOT"))

current_plot %>% 
  filter(period== 18 | period== 20 | period==22) %>% 
  ggplot( aes(y= density_dead, fill=as.factor(period))) +
  geom_boxplot()+ 
  ylab("Oyster density per m^2")+
  labs(title= "Dead Oyster Density by Strata for Periods 18, 20 and 22", fill= "Period") +
  scale_fill_manual(values=c("#CC79A7", "#E69F00", "#56B4E9"))+
  theme(legend.position="right",panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid")) +
    facet_wrap(~strata, ncol= 2)
```
Figure- Calculated dead oyster density by strata for periods 18 (Winter 2018-2019), 20 (Winter 2019-2020) and 22 (Winter 2020-2021) with the last sample date of period 22 as `r tail(org_data$date, 1)`.
\newpage


The following summary plot is calculated in R using the `geom_density` (https://ggplot2.tidyverse.org/reference/geom_density.html) statistical function in `ggplot`. The `geom_density` function computes and draws kernel density estimates, which is then represented as a smoothed version of a histogram. 

    
```{r, echo=FALSE, comment=NA, error= FALSE}

cal_den %>% 
  filter(period== 18 | period==20) %>% 
ggplot(aes(x=density, fill = as.factor(period))) +
          geom_density(size = 1.5, alpha = 0.5)+
          xlab("Oyster density per m^2")+
          ylab("Probability Density Function")+
          labs(title = "Live Oyster Density by Period (18 and 20)", fill = "Period")+
          scale_fill_manual(values=c("#CC79A7", "#E69F00"))+
          theme(panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"))

```
Figure- Calculated live oyster density by periods 18 (Winter 2018-2019) and 20 (Winter 2019-2020) using a probability density function with the last sample date of period 22 as `r tail(org_data$date, 1)`.
\newpage

```{r, echo=FALSE, comment=NA, error= FALSE}

cal_den %>% 
  filter(period== 18 | period==20) %>% 
ggplot(aes(x=density_dead, fill = as.factor(period))) +
          geom_density(size = 1.5, alpha = 0.5)+
          xlab("Oyster density per m^2")+
          ylab("Probability Density Function")+
          labs(title = "Dead Oyster Density by Period (18 and 20)", fill = "Period")+
         scale_fill_manual(values=c("#CC79A7", "#E69F00"))+
          theme(panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"))
```
Figure- Calculated dead oyster density by periods 18 (Winter 2018-2019) and 20 (Winter 2019-2020) using a probability density function with the last sample date of period 22 as `r tail(org_data$date, 1)`.
\newpage

    
```{r den_plot, echo=FALSE, comment=NA, error= FALSE}

cal_den %>% 
  filter(period== 20 | period==22) %>% 
ggplot(aes(x=density, fill = as.factor(period))) +
          geom_density(size = 1.5, alpha = 0.5)+
          xlab("Oyster density per m^2")+
          ylab("Probability Density Function")+
          labs(title = "Live Oyster Density by Period (20 and 22)", fill = "Period")+
          scale_fill_manual(values=c("#E69F00", "#56B4E9"))+
          theme(panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"))

```
Figure- Calculated live oyster density by periods 20 (Winter 2019-2020) and 22 (Winter 2020-2021) using a probability density function with the last sample date of period 22 as `r tail(org_data$date, 1)`.
\newpage

```{r, echo=FALSE, comment=NA, error= FALSE}

cal_den %>% 
  filter(period== 20 | period==22) %>% 
ggplot(aes(x=density_dead, fill = as.factor(period))) +
          geom_density(size = 1.5, alpha = 0.5)+
          xlab("Oyster density per m^2")+
          ylab("Probability Density Function")+
          labs(title = "Dead Oyster Density by Period (20 and 22)", fill = "Period")+
          scale_fill_manual(values=c("#E69F00", "#56B4E9"))+
          theme(panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"))
```
Figure- Calculated dead oyster density by periods 20 (Winter 2019-2020) and 22 (Winter 2020-2021) using a probability density function with the last sample date of period 22 as `r tail(org_data$date, 1)`.
\newpage

```{r, echo=FALSE, comment=NA, error= FALSE}

data1<- cal_den

data1$period <- factor(data1$period, levels = c("18", "20", "22"))
data1$strata <- factor(data1$strata, levels = c("Y_Y", "Y_N", "N_Y", "N_N", "N_PILOT"))

  
  data1 %>% 
    filter(period== 18 | period== 20 | period==22) %>% 
  ggplot(aes( x= count_live, y= count_dead, color= as.factor(period))) +
    geom_point(size=4) + 
    ylab("Dead Oyster Counts") +
    xlab("Live Oyster Counts") +
    labs(title= "Live and Dead Oyster Count Comparison for Periods 18, 20 and 22", color= "Period") +
     scale_color_manual(values=c("#CC79A7", "#E69F00", "#56B4E9"))+
    theme(legend.position="right",panel.grid = element_blank(), 
          panel.background = element_blank(), 
          panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"))+
    facet_wrap(~strata, ncol= 2)
```
Figure- Live and dead oyster count comparison by periods 18 (Winter 2018- 2019), 20 (Winter 2019-2020) and 22 (Winter 2020-2021), last sample date of period 22 as `r tail(org_data$date, 1)`.


```{r, echo=FALSE, fig.height = 8, fig.height = 8}
require(viridis)

data1<- cal_den

data1$strata <- factor(data1$strata, levels = c("Y_Y", "Y_N", "N_Y","N_N","N_PILOT"))

ggplot( data= data1, aes( x= count_live, y= count_dead)) +
  geom_point(size=4) + 
  ylab("Dead Oyster Counts") +
  xlab("Live Oyster Counts") +
  labs(title= "Live and Dead Count Comparison For All Periods", color= "Period") +
  #scale_color_viridis(option="heat",discrete=TRUE) +
  theme(legend.position="right",panel.grid = element_blank(), 
        panel.background = element_blank(), 
        panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid")) +
    facet_wrap(~strata, ncol= 2 )
```
Figure- Live and dead oyster comparison for all periods, last sample date of period 22 is `r tail(org_data$date, 1)`.
\newpage

